SciPy - some descriptive title here

### 2018-04-10 scipy-1.0/scipy-optimize.tex
MAINT: complete global optimization blurn

% Some problems may require the use of global optimizers to find the minimum of the objective function over the set of all parameter values, especially if the objective function possesses many local minima that other solvers could get stuck in.
% \texttt{Basinhopping} \cite{Wales1997} uses random perturbation of the parameter vector, with local minimization. The acceptance of the new coordinates is dictated by the Metropolis test typically used in Monte Carlo simulations.
% \texttt{differential\textunderscore evolution} uses

>>>>

Some problems may require the use of global optimizers to find the minimum of the objective function over the set of all parameter values, especially if the objective function possesses many local minima that other solvers could get stuck in.
\texttt{Brute} performs a grid search over the entire parameter range, with the best grid point undergoing further polishing by another solver. However, this approach becomes increasingly inefficient as the problem dimensionality increases, or if the objective function has many extrema.
\texttt{Basinhopping} \cite{Wales1997} uses random perturbation of the parameter vector, with local minimization. The acceptance of the new coordinates is dictated by the Metropolis test typically used in Monte Carlo simulations.
\texttt{differential\textunderscore evolution} \cite{Wormington1999,Storn1997} is a stochastic solver that improves by gradual evolution of a population of candidate solutions. In each iteration trial candidates are generated by combination of candidates from the existing population; if the trial candidates represent an improvement then the population is updated. \texttt{differential\textunderscore evolution} does not require that the objective function be differentiable.
%  basinhopping may need differentiable objective for the local minimization.
The SciPy benchmark suite possesses a comprehensive range of global optimization problems (196), of varying difficulties, that can be used to evaluate the performance of a particular solver. This suite is used to decide whether new solvers have good enough performance to be added to the package.
